A fault tolerant multi-server system for MMOGs

### 2010-11-05 trunk/textos/phd-prospectus/prospectus.tex
finally some more or less defined architecture and sync algorithm for the crash-stop model

The server nodes are divided in two categories: \textbf{region managers} and \textbf{region backups}. A region manager is the...

>>>>

One of the assumptions here is that the events of the game lead to a deterministic resulting game state. In other words, if the game starts in the state $S_{a}$, there is only one possible state $S_{b}$ to be reached after a sequence $E=\{e_{1}, e_{2}, ..., e_{n}\}$ of events. So, the game state may be modeled as a state machine, which is replicated across the different game server nodes. These server nodes are divided in two categories: \textbf{region managers} and \textbf{region replicas}. Each region has only one manager, who is responsible for ordering the events that happen inside that region. The region replicas have no authority to order the events -- be it players' commands or non-player events, such as the actions of AI-controlled characters --, but they can deliver and process any event $e$, as long as the game state in their memory results from every game state \textit{causally} prior to $e$. We later present the causality definition considered here.

As proposed in [cite related work], it is used here the idea of \textbf{contact servers} and \textbf{target servers}. In our architecture, the players whose avatars are in a certain region are distributed among the server nodes responsible for that region. The distribution is decided based on the network latency for each pair client-server. Each client is assigned to a server to which it has the lowest network latency among all servers in its region. This server, to which the client communicates directly, is its contact server. The target server is always the region manager, which can also be the contact server for certain players. When one of the servers gets overloaded because of the broadcasting of messages to players, these messages are then sent via other routes, even if the network latency of that new route is higher.

When a player issues a command, it is sent to its contact server, which forwards the command to the region manager. The region manager then processes the command sent by the player and calculates its resulting state, also considering commands sent by other players. Any prior event that the contact server should be aware of and that has not been received by the contact server of that player yet is then sent by the region manager.

asdf
